A Model to Predict Survival in Patients with End-Stage Liver Disease

### 2022-03-11 analysis/article.Rmd
fix: cite timeROC package

```{r knitr_setup, include=FALSE}
knitr::write_bib(
    c(
        "base",
        "targets", "workflowr",
        "gtsummary",
        "mlr3", "mlr3proba", "zlog",
        "survival", "glmnet", "penalized", "ranger", "randomForestSRC",
        "xgboost", "survivalsvm", "survivalmodels"
    ),
    file = rprojroot::find_rstudio_root_file(
        "analysis", "bibliography", "rpackages", "article.bib"
    )
)
```

@@

The final model was compared against the MELD, MELD-Na and MELD-Plus7 score
using the area under the time-dependent ROC curve (AUC)
based on the nonparametric inverse probability of censoring weighting estimator
(IPCW) [@blanche2013].

>>>>

```{r knitr_setup, include=FALSE}
knitr::write_bib(
    c(
        "base",
        "targets", "workflowr",
        "gtsummary",
        "mlr3", "mlr3proba", "zlog",
        "survival", "glmnet", "penalized", "ranger", "randomForestSRC",
        "xgboost", "survivalsvm", "survivalmodels", "timeROC"
    ),
    file = rprojroot::find_rstudio_root_file(
        "analysis", "bibliography", "rpackages", "article.bib"
    )
)
```

@@

The final model was compared against the MELD, MELD-Na and MELD-Plus7 score
using the area under the time-dependent ROC curve (AUC)
based on the nonparametric inverse probability of censoring weighting estimator
(IPCW) [@blanche2013, @R-timeROC].
